---
title: "TEFAS Fund Data Import Process"
author: "MEF BDA 503 - Champions Project Group"
date: "29 11 2020"
Output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANG = "en")
library(tidyverse)
library(lubridate)
library(readxl)
library(writexl)


```



We have downloaded historical  data of mutual funds from https://www.tefas.gov.tr/TarihselVeriler.aspx Due to the restriction we had to download in 6 files.

We will first import price data which is at the "Genel Bilgiler" sheet of the excel files.


```{r}
#import price data for each individual file

df_mk_price_2015 <- read_excel("MK-2015.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_mk_price_2016 <- read_excel("MK-2016.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_mk_price_2017 <- read_excel("MK-2017.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_mk_price_2018 <- read_excel("MK-2018.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_mk_price_2019 <- read_excel("MK-2019.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_mk_price_2020 <- read_excel("MK-2020.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()

# Append data frames and add a column whether the data is for mutual or pension fund

df_mk_price_all <- bind_rows(df_mk_price_2015, df_mk_price_2016, df_mk_price_2017, df_mk_price_2018, df_mk_price_2019, df_mk_price_2020) %>% mutate(fund_type="mutual")


```






We have downloaded historical  data of mutual funds from https://www.tefas.gov.tr/TarihselVeriler.aspx Due to the restriction we had to download in 6 files.
We will first import price data which is at the "Genel Bilgiler" sheet of the excel files.


```{r}

#import price data for each individual file


df_bes_price_2015 <- read_excel("BES-2015.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_bes_price_2016 <- read_excel("BES-2016.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_bes_price_2017 <- read_excel("BES-2017.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_bes_price_2018 <- read_excel("BES-2018.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_bes_price_2019 <- read_excel("BES-2019.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()
df_bes_price_2020 <- read_excel("BES-2020.xlsx", sheet = "Genel Bilgiler", col_types = c("date", "text", "text", "numeric", "numeric", "numeric", "numeric")) %>% glimpse()

# Append data frames and add a column whether the data is for mutual or pension fund

df_bes_price_all <- bind_rows(df_bes_price_2015, df_bes_price_2016, df_bes_price_2017, df_bes_price_2018, df_bes_price_2019, df_bes_price_2020) %>% mutate(fund_type="pension")


```


Now we will combine pension and mutual fund historical price data at a single data frame

```{r}
df_price_all <- bind_rows(df_bes_price_all, df_mk_price_all) %>%glimpse() 
```




We will import  fund portfolio allocation data for mutual  funds from the "Portföy Dağılımı" sheet, and combine them just like we did for price data.

```{r}
df_mk_portfolio_2015 <- read_excel("MK-2015.xlsx", sheet = "Portföy Dağılımı")
df_mk_portfolio_2016 <- read_excel("MK-2016.xlsx", sheet = "Portföy Dağılımı")
df_mk_portfolio_2017 <- read_excel("MK-2017.xlsx", sheet = "Portföy Dağılımı")
df_mk_portfolio_2018 <- read_excel("MK-2018.xlsx", sheet = "Portföy Dağılımı")
df_mk_portfolio_2019 <- read_excel("MK-2019.xlsx", sheet = "Portföy Dağılımı")
df_mk_portfolio_2020 <- read_excel("MK-2020.xlsx", sheet = "Portföy Dağılımı")

df_mk_portfolio_all <- bind_rows(df_mk_portfolio_2015, df_mk_portfolio_2016, df_mk_portfolio_2017, df_mk_portfolio_2018, df_mk_portfolio_2019, df_mk_portfolio_2020) %>% mutate(fund_type="mutual") %>%glimpse()
```




Now we will import pension fund portfolio allocation data for pension funds from the "Portföy Dağılımı" sheet, and combine them
```{r}
df_bes_portfolio_2015 <- read_excel("BES-2015.xlsx", sheet = "Portföy Dağılımı")
df_bes_portfolio_2016 <- read_excel("BES-2016.xlsx", sheet = "Portföy Dağılımı")
df_bes_portfolio_2017 <- read_excel("BES-2017.xlsx", sheet = "Portföy Dağılımı")
df_bes_portfolio_2018 <- read_excel("BES-2018.xlsx", sheet = "Portföy Dağılımı")
df_bes_portfolio_2019 <- read_excel("BES-2019.xlsx", sheet = "Portföy Dağılımı")
df_bes_portfolio_2020 <- read_excel("BES-2020.xlsx", sheet = "Portföy Dağılımı")

df_bes_portfolio_all <- bind_rows(df_bes_portfolio_2015, df_bes_portfolio_2016, df_bes_portfolio_2017, df_bes_portfolio_2018, df_bes_portfolio_2019, df_bes_portfolio_2020) %>% mutate(fund_type="pension") %>% glimpse()


```


combine pension and mutual fund portfolio data 
```{r}
df_portfolio_all <- bind_rows(df_bes_portfolio_all, df_mk_portfolio_all) %>% select(-"Fon Adı")%>% rename(TARİH=Tarih, "FON KODU"="Fon Kodu")%>% glimpse()
```

We can merge historical portfolio and historical price data in a single data frame, during this process we have simplified and streamlined variable names.


```{r}

df_all = full_join (df_price_all, df_portfolio_all)%>% rename(date=TARİH, 
                     code=`FON KODU`,
                     name=`FON ADI`,
                     price=FİYAT,
                     shares=`TEDAVÜLDEKİ PAY SAYISI`,
                     people=`KİŞİ SAYISI`,
                     total_value=`FON TOPLAM DEĞER`,
                     p_Bank_Bills=`Banka Bonosu (%)`,
                     p_Other=`Diğer (%)`,
                     p_FX_Payable_Bills=`Döviz Ödemeli Bono (%)`,
                     p_Government_Bond=`Devlet Tahvili (%)`,
                     p_Foreign_Currency_Bills=`Dövize Ödemeli Tahvil (%)`,
                     p_Eurobonds=`Eurobonds (%)`,
                     p_Commercial_Paper=`Finansman Bonosu (%)`,
                     p_Fund_Participation_Certificate=`Fon Katılma Belgesi (%)`,
                     p_Real_Estate_Certificate=`Gayrı Menkul Sertifikası (%)`,
                     p_Treasury_Bill=`Hazine Bonosu (%)`,
                     p_Stock=`Hisse Senedi (%)`,
                     p_Government_Bonds_and_Bills_FX=`Kamu Dış Borçlanma Araçları (%)`,
                     p_Participation_Account=`Katılım Hesabı (%)`,
                     p_Government_Lease_Certificates=`Kamu Kira Sertifikaları (%)`,
                     p_Precious_Metals=`Kıymetli Madenler (%)`,
                     p_Private_Sector_Lease_Certificates=`Özel Sektör Kira Sertifikaları (%)`,
                     p_Private_Sector_Bond=`Özel Sektör Tahvili (%)`,
                     p_Repo=`Repo (%)`,
                     p_Derivatives=`Türev Araçları (%)`,
                     p_TMM=`TPP (%)`,
                     p_Reverse_Repo=`Ters-Repo (%)`,
                     p_Asset_Backed_Securities=`Varlığa Dayalı Menkul Kıymetler (%)`,
                     p_Term_Deposit=`Vadeli Mevduat (%)`,
                     p_Foreign_Debt_Instruments=`Yabancı Borçlanma Aracı (%)`,
                     p_Foreign_Equity=`Yabancı Hisse Senedi (%)`,
                     p_Foreign_Securities=`Yabancı Menkul Kıymet (%)`)%>%glimpse()
             
```




Unfortunaley fund category data is not included at this file. TEFAS shares this data at another excel file import, fund comparison report. 
We downloaded this report from the English version of the site to get the official English translations of the categories: http://fundturkey.com.tr/FonKarsilastirma.aspx
Pension and mutual funds have separate imports.


Let's import fund comparison file to combine " fund category" data to our data set
```{r}
df_BES_compare <- read_excel("BES-compare-EN.xlsx", sheet = "Return-Based")%>%rename(code=`Fund Code`, category=`Fund Type`) %>% select(code,category)%>%glimpse()

df_MK_compare <- read_excel("MK-compare-EN.xlsx", sheet = "Return-Based")%>%rename(code=`Fund Code`, category=`Umbrella Fund Type`) %>%select(code,category)%>%glimpse()


df_compare_all <- bind_rows(df_BES_compare, df_MK_compare) %>% glimpse()
```


now lets combine them to the main data frame, also change the order of important variables close



```{r}
df_import=left_join(df_all,df_compare_all)%>%relocate(category, .after=code)%>%relocate(fund_type, .after=code)%>% glimpse()
```

We have completed our first milestone. Our last step is to export imported data not to repeat all those long steps for future work and better team co-operation.

We tested 3 formats: rds, csv, xlsx

```{r}
saveRDS(df_import, "df_import.rds")
write.csv(df_import, "df_import.csv", fileEncoding = "UTF-8") #specifying encoding is crucial to import Turkish caharacters in .csv files.
write_xlsx(df_import, "df_import.xlsx")#writexl great library utilising C for efficient xlsx uploads


```

RDS provided faster export and much smaller datafile compared with xlsx and csv. 
 RDS: 31MB
 xlsx: 123MB
 csv: 203MB

We will delete bulky xlsx and csv exports. We will keep  RDS for future work for efficiency.

You can review our raw data, exports and import steps at out google drive directory:
https://drive.google.com/drive/folders/18wJX4YufJGfuj9KWUV3YfNmxSYmhJ8WN?usp=sharing 



