---
title: "TEFAS Fund Data Exploratory Data Analysis"
author: "MEF BDA 503 - Champions Project Group"
date: "02 12 2020"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
    number_sections: true
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANG = "en")
## install.packages("writexl")
## install.packages("kableExtra")
library(tidyverse)
library(ggplot2)
library(lubridate)
library(stringr)
library(stringi)
library(kableExtra)

```

# Dataset

Read clean data set "df_clean.rds" that we produced at the previous step [Preprocessing Step 2: Data Cleaining & Transforming](champions-tefas-data-clean-transform.html)


```{r, warning=FALSE, message= FALSE}

df_all = readRDS("df_clean.rds") %>% glimpse()
```
`df_all` covers all dataset

# Overall Information about Dataset

 unique  number of funds 

```{r, warning=FALSE, message= FALSE}
df_all %>% distinct(code) %>% summarise(count=n())
```

Unique number of funds by types
```{r, warning=FALSE, message= FALSE}
df_all %>% group_by(fund_type)%>%  distinct(code) %>% summarise(count=n())
```

Unique number of funds by types and categories
```{r, warning=FALSE, message= FALSE}
df_all %>% group_by(fund_type, category)%>%  distinct(code) %>% summarise(count=n())%>%arrange(desc(count))
```



Date coverage of data: max length of our data set is 1834 days with 1262 data points. No fund data during weekends and official holidays.
```{r, warning=FALSE, message= FALSE}
df_all %>% distinct(date) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))
```


total number of data points and date coverage for each fund. Some funds have huge gaps in their data. Ratio of data points to length of time is as low as 25% for some funds while majority of funds it is over 65%. almost all of the funds with data irregularities are Hedge Umberella Funds 

```{r, warning=FALSE, message= FALSE}
df_all %>% group_by(code, fund_type,category) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=as.integer(max(date)-min(date))) %>% mutate(coverage=count/length)%>%arrange((coverage))
```

## Distribution of Fund Data Time Length by Years

107 funds has less than 1 years data

```{r, warning=FALSE, message= FALSE}
df_all %>% group_by(code) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))%>% arrange(count) %>% group_by(length_years=as.integer(floor(length/365)) )%>% summarise(countcuts=n())%>% arrange(length_years)#%>%glimpse()
```

447 funds have at least 5 calendar years of data coverage(starting from 2015-11-16 or earlier)

```{r, warning=FALSE, message= FALSE}
df_all %>% group_by(code, fund_type) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))%>%arrange(desc(earliest)) %>% filter(earliest<=ymd("2015-11-16"))
```

813 funds have at least 1 calendar years of data coverage(starting from 2019-11-15 or earlier)

```{r, warning=FALSE, message= FALSE}
df_all %>% group_by(code) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))%>%arrange((code)) %>% filter(earliest<=ymd("2019-11-15"))
```

## Daily Price Change

The `df_plot_price` dataset provides daily price change and standard deviation of the last 1 year of data. We kept only the funds which have at least 1 year of price data.


```{r, warning=FALSE, message=FALSE}
df_plot_price=df_all%>%group_by(code,fund_type,category,company_name)%>%arrange(code,date)%>%mutate(previousday=lag(price,n=1), daily_price_change=price/previousday-1)%>%filter(date>=ymd("20191115"))%>%summarise(avg_daily_change=mean(daily_price_change, na.rm = TRUE), stdev=sd(daily_price_change, na.rm = TRUE),earliest=min(date), count=n())%>%arrange(count)%>%filter(earliest<=ymd("20191118"))
df_plot_price%>%arrange(count)
```

## Annual Price Change

The `df_price_change` dataset provides annual price change (between 2019-11-15 and 2020-11-16)

```{r, warning=FALSE, message=FALSE}
df_price_change=df_all%>%filter(date==ymd("2019-11-15")|date==ymd("2020-11-16"))%>%group_by(code,fund_type,category,company_name)%>%arrange(code,date)%>%mutate(previous_price=lag(price),annual_change=price/previous_price-1)%>%relocate(annual_change)%>%filter(!is.na(annual_change))%>%select(-previous_price)
df_price_change
```

## Annual Price Change vs Daily Average Standard Deviation

Join annual price change data to daily averages and standard deviation. The `df_plot_price` dataset provides us information.
```{r, warning=FALSE, message=FALSE}
df_plot_price=left_join(df_price_change,df_plot_price%>%select(code, avg_daily_change, stdev), by="code")%>%select(-fund_type.y, -category.y)%>%rename(fund_type=fund_type.x,category=category.x)%>%relocate(avg_daily_change,stdev)%>%glimpse()
```

# Analyzes with Plots

## Annual Price Change vs Standard Deviation of Daily Change

```{r, warning=FALSE, message=FALSE}
ggplot(df_plot_price)+geom_point(aes(x=avg_daily_change, y=stdev))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(category)) +
  labs(title = 'Annual Price Change vs Daily Change Std', x='Annual Price Change', y='Daily Change Std') 
```
## Average Daily Price Change vs Standart Deviation of Daily price Change 

```{r, warning=FALSE, message=FALSE}
ggplot(df_plot_price)+geom_point(aes(x=annual_change, y=stdev))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(category)) +
  labs(title = 'Avg Daily Change vs Daily Change Std s', x='Avg Daily Change', y='Daily Change Std') 
  
```


## Annual Price Change vs Standart Deviation of Daily Change for Contribution 


```{r, warning=FALSE, messageFALSE}
ggplot(df_plot_price%>%filter(contribution==TRUE))+geom_point(aes(x=annual_change, y=stdev,color=category))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom") +
labs(title = 'Annual Price Change vs Daily Change Std of Contribution', x='Annual Price Change', y='Daily Change Std') 
```

## Annual Price Change vs Standart Deviation of Daily Change for Categories

```{r, warning=FALSE}
df_plot_categories=df_plot_price%>%group_by(category, fund_type)%>%summarize(avg_daily_change=mean(avg_daily_change,na.rm=TRUE),stdev=mean(stdev,na.rm = TRUE), annual_change=mean(annual_change,na.rm=TRUE))%>%glimpse()
ggplot(df_plot_categories)+geom_point(aes(x=annual_change, y=stdev, color=category))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(fund_type)) +
  labs(title = 'Annual Price Change vs Daily Change Std for Categories', x='Annual Price Change', y='Daily Change Std') 
```

## Annual Price Change vs Standart Deviation of Daily Change for Companies

```{r, warning=FALSE}
df_plot_companies=df_plot_price%>%group_by(company_name, fund_type)%>%summarize(avg_daily_change=mean(avg_daily_change,na.rm=TRUE),stdev=mean(stdev,na.rm = TRUE), annual_change=mean(annual_change,na.rm=TRUE))
ggplot(df_plot_companies)+geom_point(aes(x=annual_change, y=stdev, color=company_name))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(fund_type)) +
  labs(title = 'Annual Price Change vs Daily Change Std for Companies', x='Annual Price Change', y='Daily Change Std') 
```


```{r, warning=FALSE}
## ggplot(df_plot_categories)+geom_point(aes(x=price_change, ## y=sd_mean))+scale_x_log10()#+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")
```


## Distibution of Funds Valuation For Contribution


```{r, warning=FALSE}
df_today=df_all %>% filter(date==ymd("2020-11-16"))%>%mutate(total_value_millions=round(total_value/1000000,2), total_value_bins=floor(total_value/10000000))
ggplot(df_today)+geom_histogram(bins=50,aes(x=total_value_millions))+facet_grid(rows=vars(contribution)) +
    labs( x='Total Value in Million', y='Count') 
```


## Distibution of Number of People in Funds For Fund Types 


```{r, warning=FALSE}
df_today_investors=df_all %>% filter(date==ymd("2020-11-16"))
ggplot(df_today_investors)+geom_histogram(bins=50,aes(x=people))+facet_wrap(vars(fund_type)) +
  labs( x='People', y='Count') 
```


# Funds Comparison in Last 1 Year

We compared funds and categories based on price change in last one year. Firstly, we created datasets for analyzes

```{r, warning=FALSE}
df_2 = df_all %>%
  filter(date == ymd("2019-11-18") | date == ymd("2020-11-16")) %>%
  select(date,fund_type, category, code, company_name ,name, total_value, price) %>%
  arrange(code, name, date)
df_3 = df_2 %>%
  group_by(code, name) %>%
  mutate(previous_price=as.numeric(lag(price,n=1)), 
         change_price_percentage=100*(price-as.numeric(lag(price,n=1)))/ as.numeric(lag(price,n=1)),
         previous_total_value = as.numeric(lag(total_value,n=1)),
         change_total_value_percentage=100*(total_value-as.numeric(lag(total_value,n=1)))/ as.numeric(lag(total_value,n=1)))%>%
  filter(date==ymd('2020-11-16')) %>%
  select(date,fund_type, category, code, name, price, previous_price, change_price_percentage, total_value, previous_total_value,change_total_value_percentage )
```

## Most Valued 40 Funds

```{r, warning=FALSE}
order_price_best = df_3 %>%
  arrange(desc(change_price_percentage)) %>%
  select(fund_type, category, code, name, previous_price, price, change_price_percentage)
best_price_funds=order_price_best[1:40, ]
best_price_funds
```


The `best_category` shows distribution of the fund categories of most 40 valued funds for last 1 year

```{r, warning=FALSE}
best_category = best_price_funds %>%
  group_by(category) %>%
  count(category) %>%
  arrange(desc(n))
```

```{r tables}
kable(best_category, col.names = c("Fund Category", "Number of Funds"))
```

## Least Valued / Depreciated 40 Funds

```{r, warning=FALSE}
order_price_worst = df_3 %>%
  arrange(change_price_percentage) %>%
  select(fund_type, category, code, name, previous_price, price, change_price_percentage)
worst_price_funds=order_price_worst[1:40, ]
worst_price_funds
```


The `wors_category` shows distribution of the fund categories of least valued / depreciated 40 funds for last 1 year

```{r, warning=FALSE}
worst_category = worst_price_funds %>%
  group_by(category) %>%
  count(category) %>%
  arrange(desc(n))
```

```{r tables 2}
kable(worst_category, col.names = c("Fund Category", "Number of Funds"))
```