---
title: "Champions Project-CK work"
author: "Cagatay Kiyici"
date: "19 11 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANG = "en")
library(tidyverse)
library(ggplot2)
library(lubridate)
library(readxl)
library(stringr)
library(stringi)

library(writexl)
#library(WriteXLS)


```

Read imported data set
```{r}
df_all = readRDS("df_clean_2.1.rds") %>% glimpse()

```


 unique  number of funds 

```{r}

df_all %>% distinct(code) %>% summarise(count=n())

```

Unique number of funds by types
```{r}

df_all %>% group_by(fund_type)%>%  distinct(code) %>% summarise(count=n())

```

Unique number of funds by types and categories
```{r}

df_all %>% group_by(fund_type, category)%>%  distinct(code) %>% summarise(count=n())%>%arrange(desc(count))

```



Date coverage of data: max length of our data set ise 1834 days with 1262 data points. No fund data during weekends and official holidays.
```{r}

df_all %>% distinct(date) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))


```


total number of data points and date coverage for each fund. Some funds have huge gaps in their data. Ratio of data points to length of time is as low as 25% for some funds while majority of funds it is over 65%. almost all of the funds with data irregularities are Hedge Umberella Funds 

```{r}

df_all %>% group_by(code, fund_type,category) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=as.integer(max(date)-min(date))) %>% mutate(coverage=count/length)%>%arrange((coverage))


```



What is the distribution of fund data time length by years? 107 funds has less than 1 years data

```{r}

df_all %>% group_by(code) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))%>% arrange(count) %>% group_by(length_years=as.integer(floor(length/365)) )%>% summarise(countcuts=n())%>% arrange(length_years)#%>%glimpse()

```

How many funds have at lease 5 calendar years of data coverage(starting from 2020-11-16 or earlier)? 447 funds


```{r}

df_all %>% group_by(code, fund_type) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))%>%arrange(desc(earliest)) %>% filter(earliest<=ymd("2015-11-16"))


```

How many funds have at least 1 calendar years of data coverage(starting from 2019-11-15 or earlier)? 813 funds. 


```{r}

df_all %>% group_by(code) %>% summarise(count=n(), latest=max(date), earliest=min(date), length=max(date)-min(date))%>%arrange((code)) %>% filter(earliest<=ymd("2019-11-15"))

```



Let s calculate daily price change and standard deviation of the last 1 year of data. We kept only the funds which have at least 1 year of price data.


```{r}
df_plot_price=df_all%>%group_by(code,fund_type,category,company_name)%>%arrange(code,date)%>%mutate(previousday=lag(price,n=1), daily_price_change=price/previousday-1)%>%filter(date>=ymd("20191115"))%>%summarise(avg_daily_change=mean(daily_price_change, na.rm = TRUE), stdev=sd(daily_price_change, na.rm = TRUE),earliest=min(date), count=n())%>%arrange(count)%>%filter(earliest<=ymd("20191118"))


df_plot_price%>%arrange(count)



```



Calculate annual price change (between 2019-11-15 and 2020-11-16)

```{r}
df_price_change=df_all%>%filter(date==ymd("2019-11-15")|date==ymd("2020-11-16"))%>%group_by(code,fund_type,category,company_name)%>%arrange(code,date)%>%mutate(previous_price=lag(price),annual_change=price/previous_price-1)%>%relocate(annual_change)%>%filter(!is.na(annual_change))%>%select(-previous_price)
df_price_change

```


Join annual price change data to daily averages and standard deviation
```{r}
df_plot_price=left_join(df_price_change,df_plot_price%>%select(code, avg_daily_change, stdev), by="code")%>%select(-fund_type.y, -category.y)%>%rename(fund_type=fund_type.x,category=category.x)%>%relocate(avg_daily_change,stdev)%>%glimpse()

```



```{r}


ggplot(df_plot_price)+geom_point(aes(x=avg_daily_change, y=stdev))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(category)) 


```


```{r}


ggplot(df_plot_price)+geom_point(aes(x=annual_change, y=stdev))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(category)) 


```





```{r}


ggplot(df_plot_price%>%filter(contribution==TRUE))+geom_point(aes(x=annual_change, y=stdev,color=category))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")#+facet_wrap(vars(contribution)) 


```



```{r}
df_plot_categories=df_plot_price%>%group_by(category, fund_type)%>%summarize(avg_daily_change=mean(avg_daily_change,na.rm=TRUE),stdev=mean(stdev,na.rm = TRUE), annual_change=mean(annual_change,na.rm=TRUE))%>%glimpse()



ggplot(df_plot_categories)+geom_point(aes(x=annual_change, y=stdev, color=category))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(fund_type)) 



```
```{r}
df_plot_companies=df_plot_price%>%group_by(company_name, fund_type)%>%summarize(avg_daily_change=mean(avg_daily_change,na.rm=TRUE),stdev=mean(stdev,na.rm = TRUE), annual_change=mean(annual_change,na.rm=TRUE))


ggplot(df_plot_companies)+geom_point(aes(x=annual_change, y=stdev, color=company_name))+scale_x_log10()+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")+facet_wrap(vars(fund_type)) 



```


```{r}

ggplot(df_plot_categories)+geom_point(aes(x=price_change, y=sd_mean))+scale_x_log10()#+scale_y_log10()+theme_minimal()+theme(legend.position="bottom")

```










How is the valuation of the funds distributed?


```{r}

df_today=df_all %>% filter(date==ymd("2020-11-16"))%>%mutate(total_value_millions=round(total_value/1000000,2), total_value_bins=floor(total_value/10000000))



ggplot(df_today)+geom_histogram(bins=50,aes(x=total_value_millions))+facet_grid(rows=vars(contribution))
```





```{r}

df_today_investors=df_all %>% filter(date==ymd("2020-11-16"))#>%mutate(total_value_millions=round(total_value/1000000,2), total_value_bins=floor(total_value/10000000))



ggplot(df_today_investors)+geom_histogram(bins=50,aes(x=people))+facet_wrap(vars(fund_type))
```

```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```



```{r}



```


```{r}

#saveRDS(df_all,"df_clean_2.rds")

```

















